---
title: "Practical Machine Learning Course Project"
author: "Binesh Shrestha"
output: html_document
---

# Coursera Practical Machine Learning Assignment: Writeup
## Assignment
In this assignment we need to develop a machine learning model to predict the type of exercise performed based on different types of measurements given. We are given two files: **training** and **testing**. The first file is the training file, used to develop our algorithm, and the second is used to make our final predictions.

**Link to Training Data** https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv

**Link to Testing Data** https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv

##Load the Data
First of all, we download the both sets of data and place it in the current working directory.We then perform basic exploratory data analysis. However, before hand we have to drop all the rows in data with **NA** values.

```{r}
setwd("D:/R/R_Assignment/MachineLearning")
a=read.csv('pml-training.csv',na.strings=c('','NA'))
b=a[,!apply(a,2,function(x) any(is.na(x)) )]
c=b[,-c(1:7)]
dim(c)
```
After applying the NA removal, we now have 19622 observatiobs and 53 predictions

we now down the necessary packages, install them and use them for further analysis.

```{r eval= FALSE}
install.packages('randomForest')
install.packages('caret')
install.packages('e1071')
```

```{r}
library('randomForest')
library('caret')
library('e1071')
```

For cross validation, We split our testing data into sub groups, 60:40
```{r}
subGrps=createDataPartition(y=c$classe, p=0.6, list=FALSE)
subTraining=c[subGrps,]
subTesting=c[-subGrps, ]
dim(subTraining);dim(subTesting)
```
We see there are 11776  in the subTraining group, and 7846 in the subTesting group.

we now make a predictive model based on the forest paradigm.

```{r}
model=randomForest(classe~., data=subTraining, method='class')
pred=predict(model,subTesting, type='class')
z=confusionMatrix(pred,subTesting$classe)
save(z,file='test.RData')
```

we now load the test.RData file
```{r}
load('test.RData')
z$table
z$overall[1]
```

Based on this, The accuracy is 99.49%. The out of sample error, that is the error rate on a new (subTesting) data set, here is going to be 0.51%, with a 95% confidence interval of 0.52% to .9%.

## Final Data Set Analysis and Predictions

we now continue with the final testing data set, and proceed as before.
```{r}
d=read.csv('pml-testing.csv',na.strings=c('','NA'))
e=d[,!apply(d,2,function(x) any(is.na(x)) )]
f=e[,-c(1:7)]
dim(f)
```

after the data processed, we analize it using previous model developed
```{r}
predicted=predict(model,f,type='class')
save(predicted,file='predicted.RData')
```

The final prediction for the 20 ends up as:
```{r}
load('predicted.RData')
predicted
```

The Prediction is as: 
## B  A  B  A  A  E  D  B  A  A  B  C  B  A  E  E  A  B  B  B 
